---
title: "Additional analysis of beta-diversity trends requested by reviewer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Additional analysis of beta-diversity trends requested by reviewer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

load in packages
```{r, eval=FALSE}
library(CoreMicro)
library(gt)
library(tidyr)
library(tidyverse)
library(parallelDist)
library(vegan)
```

Assign core status to combine dataframes for PERMANOVA testing (adonis) and ordinations. 

hard cutoff core
```{r, eval=FALSE}
hcT<-hard_cutoff(arabidopsis_rhizo, cutoff = 25, sites = 5)
arabidopsis_hcT <- arabidopsis_rhizo[arabidopsis_rhizo$X %in% hcT,]
names(arabidopsis_hcT) <- paste(names(arabidopsis_hcT), "_hcT", sep = "")
names(arabidopsis_hcT)[1] <- "X"
```

abundance based core
```{r, eval=FALSE}
psT<-abundance_core(arabidopsis_rhizo, readn = 0.75)
arabidopsis_psT <- arabidopsis_rhizo[arabidopsis_rhizo$X %in% psT,]
names(arabidopsis_psT) <- paste(names(arabidopsis_psT), "_pst", sep = "")
names(arabidopsis_psT)[1] <- "X"
arabidopsis_rhizo[arabidopsis_rhizo$X %in% psT,]
```

occupancy based core
```{r, eval=FALSE}
prT<-occupancy_core(arabidopsis_rhizo, prop_rep =  0.5)

arabidopsis_prT <- arabidopsis_rhizo[arabidopsis_rhizo$X %in% prT,]
names(arabidopsis_prT) <- paste(names(arabidopsis_prT), "_prt", sep = "")

names(arabidopsis_prT)[1] <- "X"
```

abundance and occupancy based core
```{r, eval=FALSE}
prrT<-abundance_and_occupancy_core(arabidopsis_rhizo, prop_rep =  0.5, prop_reads = 0.0002)

arabidopsis_prrT <- arabidopsis_rhizo[arabidopsis_rhizo$X %in% prrT,]
names(arabidopsis_prrT) <- paste(names(arabidopsis_prrT), "_prrt", sep = "")
names(arabidopsis_prrT)[1] <- "X"

#pullout mean and variance to use when parameterizing dm draws in simulations
core_abundance <- summarise_taxa(arabidopsis_rhizo[arabidopsis_rhizo$X %in% prrT,]) %>% summary() %>% data.frame() 
non_core_abundance <- summarise_taxa(arabidopsis_rhizo[!(arabidopsis_rhizo$X %in% prrT),]) %>% summary()


#core_abundance[core_abundance$Var2 == "     Mean"]
#core_abundance[10,3]
```

combine 4 core datasets to create one dataframe for PERMANOVA
```{r, eval=FALSE}
names(arabidopsis_rhizo) <- paste(names(arabidopsis_rhizo), "_full", sep = "")
names(arabidopsis_rhizo)[1] <- "X"
merged_datasets<-full_join(arabidopsis_prrT, arabidopsis_prT, by = "X") %>% full_join(arabidopsis_hcT) %>% full_join(arabidopsis_psT) %>% full_join(arabidopsis_rhizo) 
merged_datasets <- data.frame(merged_datasets)
merged_datasets[is.na(merged_datasets)] <- 0
rownames(merged_datasets)<-merged_datasets$X
merged_datasets$X = NULL
merged_datasets_matrix<-as.matrix(merged_datasets)
merged_datasets_matrix_t <- t(merged_datasets_matrix)
```

calculate bray-curtis dissimilarity, run tests of dispersion, adonis, and plot 
```{r, eval=FALSE}
dist<-parDist(merged_datasets_matrix_t, method = "bray")
sd <- data.frame(rownames(merged_datasets_matrix_t))
rownames(sd) <- rownames(merged_datasets_matrix_t)
sd$CoreMethods <- str_sub(rownames(sd), start= -4)
unique(sd$CoreMethods)
anova(betadisper(dist, sd$CoreMethods, type = "centroid"))
plot(betadisper(dist, sd$CoreMethods, type = "centroid"), main = "Arabidopsis")
boxplot(betadisper(dist, sd$CoreMethods, type = "centroid"))
adonis2(dist ~ CoreMethods, data = sd, permutations = 100)
#pairwise.adonis(dist, factors = sd$CoreMethods, perm = 1000)
```

##Rerun all analysis for human microbiome project

hard cutoff core
```{r, eval=FALSE}
names(human_stool)[1] <- "X"
hcT<-hard_cutoff(human_stool, cutoff = 25, sites = 5)
human_stool_hcT <- human_stool[human_stool$X %in% hcT,]
names(human_stool_hcT) <- paste(names(human_stool_hcT), "_hcT", sep = "")
names(human_stool_hcT)[1] <- "X"
```

abundance based core
```{r, eval=FALSE}
psT<-abundance_core(human_stool, readn = 0.75)
human_stool_psT <- human_stool[human_stool$X %in% psT,]
names(human_stool_psT) <- paste(names(human_stool_psT), "_pst", sep = "")
names(human_stool_psT)[1] <- "X"
```

occupancy based core
```{r, eval=FALSE}
prT<-occupancy_core(human_stool, prop_rep =  0.5)
human_stool_prT <- human_stool[human_stool$X %in% prT,]
names(human_stool_prT) <- paste(names(human_stool_prT), "_prt", sep = "")
names(human_stool_prT)[1] <- "X"
```

abundance and occupancy based core
```{r, eval=FALSE}
prrT<-abundance_and_occupancy_core(human_stool, prop_rep =  0.5, prop_reads = 0.0002)
human_stool_prrT <- human_stool[human_stool$X %in% prrT,]
names(human_stool_prrT) <- paste(names(human_stool_prrT), "_prrt", sep = "")
names(human_stool_prrT)[1] <- "X"
```

combine 4 core datasets to create one dataframe for PERMANOVA
```{r, eval=FALSE}
names(human_stool) <- paste(names(human_stool), "_full", sep = "")
names(human_stool)[1] <- "X"
merged_datasets<-full_join(human_stool_prrT, human_stool_prT, by = "X") %>% full_join(human_stool_hcT) %>% full_join(human_stool_psT) %>% full_join(human_stool) 
merged_datasets <- data.frame(merged_datasets)
merged_datasets[is.na(merged_datasets)] <- 0
rownames(merged_datasets)<-merged_datasets$X
merged_datasets$X = NULL
merged_datasets_matrix<-as.matrix(merged_datasets)
merged_datasets_matrix_t <- t(merged_datasets_matrix)
```

calculate bray-curtis dissimliarity, run tests of dispersion, adonis, and plot
```{r, eval=FALSE}
sd <- data.frame(rownames(merged_datasets_matrix_t))
rownames(sd) <- rownames(merged_datasets_matrix_t)
sd$CoreMethods <- str_sub(rownames(sd), start= -4)
unique(sd$CoreMethods)
dist<-parDist(merged_datasets_matrix_t, method = "bray")
anova(betadisper(dist, sd$CoreMethods, type = "centroid"))
plot(betadisper(dist, sd$CoreMethods, type = "centroid"), main = "human")
boxplot(betadisper(dist, sd$CoreMethods, type = "centroid"))
#pairwise.adonis(dist, factors = sd$CoreMethods, perm = 1000)
adonis2(dist ~ CoreMethods, data = sd, permutations = 100)
```
