---
title: "Common Counts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Common Counts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(CoreMicro)
```

This is a thought for antoher function. 
This would table counts of each method so we have an idea of the size of inclusion by each

It may already be included in another funciton though and could just be an intermediate output. 

#arabidopsis

```{r eval=FALSE}
arab_core<-core_methods(arabidopsis)
arab_core_df<- data.frame(arab_core)
table(arab_core_df$name, arab_core_df$value)
```

# Create table all taxa that are never assigned.
```{r, eval=FALSE}
wide_arab<-pivot_wider(arab_core_df)
table(rowSums(wide_arab[,5:8]))
wide_arab$num_methods<-(rowSums(wide_arab[,5:8]))
#tables number assigned by each method
table(wide_arab$`Summation of Sequence Reads`)
table(wide_arab$`Proportion of Sequence Reads and Replicates`)
table(wide_arab$`Hard Cutoff`)
table(wide_arab$`Proportion of Sequence Replicates`)
```

#pull out those common taxa found by all
```{r, eval=FALSE}
(wide_arab[wide_arab$num_methods==4,])$X
pull out those taxa included by each method
prop_seq_reads_core<-(wide_arab[wide_arab$`Proportion of Sequence Reads`==1,])$X
```

```{r, eval=FALSE}
prop_seq_readsnrep_core<-(wide_arab[wide_arab$`Proportion of Sequence Reads and Replicates`==1,])$X

HC_core<-(wide_arab[wide_arab$`Hard Cut Off`==1,])$X

prop_rep_core<-(wide_arab[wide_arab$`Proportion of Sequence Replicates`==1,])$X
```

```{r, eval=FALSE}
X<-as.character(rownames(otu_human_a))
otu_human_a<-cbind(X, otu_human_a)
rownames(otu_human_a)=NULL
names(otu_human_a)
rownames(otu_human_a)
```

#HMBP

```{r, eval=FALSE}
#human_tib<-as_tibble(otu_human_a)
human_core<-core_methods(human_otu, taxa_as_rows = T)
human_core_df<- data.frame(human_core)
table(human_core_df$name, human_core_df$value)
```

# Create table all taxa that are never assigned.

```{r, eval=FALSE}
wide_human<-pivot_wider(human_core_df)
table(rowSums(wide_human[,5:8]))
#tables number assigned by each method
table(wide_human$`Summation of Sequence Reads`)
table(wide_human$`Proportion of Sequence Reads and Replicates`)
table(wide_human$`Hard Cutoff`)
table(wide_human$`Proportion of Sequence Replicates`)
```
